--- 
title: "An introduction to Statistical Modelling using GLMs"
author: "Lindesay Scott-Hayward"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: 
  bookdown::gitbook:
    lib_dir: "book_assets"
    config:
      sharing: null
      fontsettings:
        theme: Sepia
        size: 2
      edit: null
    split_by: section
    highlight: tango
  bookdown::pdf_book:
    keep_tex: yes
    citation_package: natbib
    latex_engine: xelatex
    includes:
      in_header: preamble.tex
      after_body: afterbody.tex
  bookdown::word_document2:
    toc: true
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: lindesaysh/StatmodellingGitBook
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Course Information

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
